Intro Seminar

### 2017-03-22 doc/seminar2017.Rmd
Fixed plot axis label

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, echo = FALSE, message = FALSE, warning = FALSE)
library(dplyr)
devtools::load_all()
load_data(update = TRUE)
set_options()
```

@@

ds %>% 
  # dplyr::filter(eGFR < 150) %>% 
  dplyr::filter(fVN == "Baseline") %>% 
  dplyr::select(eGFR, udbpCrRatio) %>% 
  na.omit() %>% 
  scatter_plot("eGFR", "log(udbpCrRatio)",
               "Estimated Glomerular Filtration Rate (ml/min/1.73m^2)",
               "log UDBP:Creatinine (ug/mmol)")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, echo = FALSE, message = FALSE, warning = FALSE)
library(dplyr)
devtools::load_all()
load_data(update = TRUE)
set_options()
extrafont::loadfonts(device="win")
```

@@

ds %>% 
  # dplyr::filter(eGFR < 150) %>% 
  dplyr::filter(fVN == "Baseline") %>% 
  dplyr::select(eGFR, udbpCrRatio) %>% 
  na.omit() %>% 
  scatter_plot("eGFR", "log(udbpCrRatio)",
               "Estimated Glomerular Filtration Rate (ml/min/1.73m^2)",
               "log uVDBP:Creatinine (ug/mmol)")
